---
title: "ED Scale Feb 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

### To-Do List

* Load class data
* Specify our measurement model
    * Unidimensional
    * Multidimensional
* Specify full model (all nine indicators)
* Reduce the model to
    * Non-significant Chi-square
    * No measurement error covariances
    * Squared lambda greater than .5
        * Standardized lambda > .7
        
        
### Load Data

```{r}
library(tidyverse)

# Access course data

eo.ds <- read_csv("http://www.drbanderson.com/data/ENT5587C_Spring2018.csv")

eo.df <- eo.ds %>%
  dplyr::select(INN1:RISK3) %>% 
  na.omit()
```

### Specify unidimensional measurement model

* Reflective measurement model
* Arrows from EO to its indicators
    * Change in EO reflects in the same way, and same magnitude to its indicators
* All nine indicators load on a single latent construct

### Specify multidemtional measurement model

* Reflective measurement model
* Arrows from EO to its dimensions (Innovativeness, Pro, RiskTaking)
    * Arrows from the dimensions to its indicators
* Three indicators per dimension

### Specify Full Unidimensional CFA

We're going to start with a quick distribution check of the EO indicators...

```{r}
library(skimr)

# Distribution analysis of the indicators
skim(eo.df)
```

Seems to be skewed to the more entrepreneurial end of the scale. Might need to watch that.

Next up, a CFA...

```{r}
library(lavaan)

# Specify unidemsional (nine indicators) CFA syntax
eo.cfa.full.syntax <- 'EO =~ INN1 + INN2 +INN3 + PRO1 + PRO2 + PRO3 + RISK1 + RISK2 + RISK 3'

# Specify the full CFA
eo.cfa.full.model <- sem(eo.cfa.full.syntax, data=eo.df, std.lv = TRUE)

summary(eo.cfa.full.model)
```
Now lets check the modification indicies and see the source of misspecification

```{r}
modificationIndices(eo.cfa.full.model, sort = TRUE, minimum.value = 3.84)
```

