---
title: "ED Scale Feb 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

### To-Do List

* Load class data
* Specify our measurement model
    * Unidimensional
    * Multidimensional
* Specify full model (all nine indicators)
* Reduce the model to
    * Non-significant Chi-square
    * No measurement error covariances
    * Squared lambda greater than .5
        * Standardized lambda > .7
        
        
### Load Data

```{r}
library(tidyverse)

# Access course data

eo.ds <- read_csv("http://www.drbanderson.com/data/ENT5587C_Spring2018.csv")

eo.df <- eo.ds %>%
  dplyr::select(INN1:RISK3) %>% 
  na.omit()
```

### Specify unidimensional measurement model

* Reflective measurement model
* Arrows from EO to its indicators
    * Change in EO reflects in the same way, and same magnitude to its indicators
* All nine indicators load on a single latent construct

### Specify multidemtional measurement model

* Relfective measurement model
* Arrows from EO to its dimensions (Innovativeness, Pro, RiskTaking)
    * Arrows from the dimensions to its indicators
* Three indicators per dimension

