---
title: "Lab 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Testing an hypothesis using SEM.

> Innovativeness, Proactively, and Risktaking Jointly and Positively Influence Firm Performance

### Project Tasks

* Figure out SEM
    * Four spaces do this, SEM stands for SEM --- DONE
* Import Data, Load Our Data --- DONE
* Specify Model Equation --- DONE
* Evaluated Variables --- DONE
* Variable and Initial Model Visualization
* Specify SEM Workflow
    * Specify Model Syntax and Check With Equation
* Run the Model
* Model Robustness Checks
    * Chi-squared
    * Modification Indices
    * (Lambda Loadings)
* Create Results Table

***

### Load our data

```{r}
# Access the course data from drbanderson.com
library(tidyverse)
Lab2data.ds <- read.csv("http://www.drbanderson.com/data/ENT5587C_Spring2018.csv")
head(Lab2data.ds, 10)
```

***

### Specify model equation

$Performance=\alpha+\beta_{Innovativeness}+\beta_{Proactiveness}+\beta_{RiskTaking}+\epsilon$

***
### Evaluation variables

```{r}
# create the innovativeness, proactiveness, and risk taking variables and select only varibles I need

Lab2data.df <- Lab2data.ds %>%
  mutate(Innovativeness = (INN2+INN2+INN3) / 3,
         Proactiveness = (PRO1+PRO2+PRO3) / 3,
         RiskTaking = (RISK1+RISK2+RISK3) / 3) %>%
  select(FirmID, Performance, Innovativeness, Proactiveness, RiskTaking)
```

Next we evaluate the distribution of the variables

```{r}
library(skimr)
skim(Lab2data.df)
```

