---
title: "March 19"
output: html_document
---
```{r}
library(tidyverse)
ENT5587_Exp.df <- read_csv("http://www.drbanderson.com/data/ENT5587Experiment.csv")

ENT5587_Exp.df
```

The five steps of Bayesian analysis…

Specify a prior distribution for θθ (and other unknown parameters)

Specify a joint distribution based on multiplying the prior by the likelihood function

Draw from the posterior distribution to create an estimate for θθ and all other unknown parameters

Evaluate model fit and make changes to the model

Visualize predicted probabilities based on meaningful values of the predictor variables

We are interested in whether having an entrepreneurial manager increases a person’s creativity.

```{r}
summary(lm(Creativity ~ EntManager, data = ENT5587_Exp.df))
```

```{r}
library(rstanarm)

creativity.seed <- set.seed(08022003)


creativity.model <- stan_lm(Creativity ~ EntManager * TaskSpecificity, data = ENT5587_Exp.df,
                            prior = R2(location = 0.2, what = "median"), 
                            chains = 5, iter = 10000, seed = creativity.seed)
```

```{r}
prior_summary(creativity.model)
```

```{r}
print(creativity.model, digits = 3)
```

```{r}
posterior_interval(creativity.model, prob = 0.95)
```

```{r}
creativity.noint.model <- update(creativity.model, formula = . ~ EntManager + TaskSpecificity)
```

```{r}
library(loo)

creativity.model.loo <- loo(creativity.model)
creativity.noint.model.loo <- loo(creativity.noint.model)

creativity.model.loo$looic

creativity.noint.model.loo$looic

compare_models(creativity.model.loo, creativity.noint.model.loo)
```

```{r}
pp_check(creativity.noint.model, plotfun = "hist", nreps = 5)
```

```{r}
library(bayesplot)

# The first thing we need to do is to store our posterior draws as an array...
creativity.noint.model.posterior <- as.array(creativity.noint.model)

color_scheme_set("blue")
mcmc_intervals(creativity.noint.model.posterior, 
               pars = c("EntManager", "TaskSpecificity")) + 
  theme_bw()
```

```{r}
mcmc_hist(creativity.noint.model.posterior, 
          pars = c("EntManager", "TaskSpecificity")) + 
  theme_bw()
```

```{r}
# Baseline condition
baseline.df <- as.data.frame(posterior_predict(creativity.noint.model, 
                                               newdata = data.frame(EntManager = 0, TaskSpecificity = 0)))
colnames(baseline.df) <- c("PredProb")


# Ent Manager only condition
entmanag.df <- as.data.frame(posterior_predict(creativity.noint.model, 
                                               newdata = data.frame(EntManager = 1, TaskSpecificity = 0)))
colnames(entmanag.df) <- c("PredProb")

# Task specificity only condition
taskspec.df <- as.data.frame(posterior_predict(creativity.noint.model, 
                                               newdata = data.frame(EntManager = 0, TaskSpecificity = 1)))
colnames(taskspec.df) <- c("PredProb")

# Joint condition
joint.df <- as.data.frame(posterior_predict(creativity.noint.model, 
                                            newdata = data.frame(EntManager = 1, TaskSpecificity = 1)))
colnames(joint.df) <- c("PredProb")
```
```{r}
# Get our median predicted probability
baseline.med.predprob <- round(median(baseline.df$PredProb), 3)
sub.baseline <- paste0("Median Predicted Probability: ", baseline.med.predprob)

# Now build our plot
baseline.plot <- ggplot(data = baseline.df, aes(PredProb)) + 
  geom_histogram() + 
  geom_vline(xintercept = baseline.med.predprob, linetype = "dashed", 
             color = "red", size = 1) + 
  labs(title = "Baseline Model",
       subtitle = sub.baseline,
       y = "Posterior Draws",
       x = "Predicted Probability of Creativity") + 
  theme_bw()
```
```{r}
# Get our median predicted probability
entmanag.med.predprob <- round(median(entmanag.df$PredProb), 3)
sub.entmanag <- paste0("Median Predicted Probability: ", entmanag.med.predprob)

# Now build our plot
entmanag.plot <- ggplot(data = entmanag.df, aes(PredProb)) + 
  geom_histogram() + 
  geom_vline(xintercept = entmanag.med.predprob, linetype = "dashed", 
             color = "red", size = 1) + 
  labs(title = "Entrepreneurial Manager Only",
       subtitle = sub.entmanag,
       y = "Posterior Draws",
       x = "Predicted Probability of Creativity") + 
  theme_bw()
```
```{r}
# Get our median predicted probability
taskspec.med.predprob <- round(median(taskspec.df$PredProb), 3)
sub.taskspec <- paste0("Median Predicted Probability: ", taskspec.med.predprob)

# Now build our plot
taskspec.plot <- ggplot(data = taskspec.df, aes(PredProb)) + 
  geom_histogram() + 
  geom_vline(xintercept = taskspec.med.predprob, linetype = "dashed", 
             color = "red", size = 1) + 
  labs(title = "Task Specificity Only",
       subtitle = sub.taskspec,
       y = "Posterior Draws",
       x = "Predicted Probability of Creativity") + 
  theme_bw()
```
```{r}
# Get our median predicted probability
joint.med.predprob <- round(median(joint.df$PredProb), 3)
sub.joint <- paste0("Median Predicted Probability: ", joint.med.predprob)

# Now build our plot
joint.plot <- ggplot(data = joint.df, aes(PredProb)) + 
  geom_histogram() + 
  geom_vline(xintercept = joint.med.predprob, linetype = "dashed", 
             color = "red", size = 1) + 
  labs(title = "Joint Model",
       subtitle = sub.joint,
       y = "Posterior Draws",
       x = "Predicted Probability of Creativity") + 
  theme_bw()
```
```{r}
library(gridExtra)
grid.arrange(baseline.plot, entmanag.plot, taskspec.plot, joint.plot, ncol = 2)
```
```{r}
color_scheme_set("mix-blue-red")
mcmc_trace(creativity.noint.model.posterior, pars = c("EntManager", "TaskSpecificity"),
           facet_args = list(ncol = 1, strip.position = "left"))
```

```{r}
library(blavaan)
model <- '# latent variable definitions
          ind60 =~ x1 + x2 + x3
          dem60 =~ y1 + a*y2 + b*y3 + c*y4
          dem65 =~ y5 + a*y6 + b*y7 + c*y8
     
          # regressions
          dem60 ~ ind60
          dem65 ~ ind60 + dem60
     
          # residual correlations
          y1 ~~ y5
          y2 ~~ y4 + y6
          y3 ~~ y7
          y4 ~~ y8
          y6 ~~ y8'

fit <- bsem(model, data = PoliticalDemocracy, target = "stan")
```

